Tampering Detection In Low-Power Smart Cameras

### 2015-05-28 paper.tex
Aggiunti plot nuovi

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Behavior of the average norm of the gradient \textbf{(a)} and its detrending \textbf{(b)} in a sequence with a defocus event.
The tampering event come at $t = 600$.
As illustrated in \textbf{(a)}, even in the case in which there aren't tampering events, there is nonstationarity.
Detrending is done in order to preserve stationarity in normal situations.
Considering the detrending \textbf{(b)} persistent changes become instantaneous:
in particular there is a peak in the instant in which tampering begins.}
\label{fig:indicatori} 
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Example of displacement and behavior of the average value of the luma. The event comes at frame $157$ and the corresponding value of $l(t)$ is depicted with a red star. \textbf{(a)} Considering the average value of the luma in the whole scene. \textbf{(b)} and \textbf{(c)} Considering the average value of the luma in a specific region.}
\label{fig:indicatori} 
\end{figure}
